Time slice analyses

### 2017-12-15 analyses/02-time-slice-analyses.Rmd
Change branch for dipRity install
Order slugs so it  matches later analyses and remove bears

This code runs the analyses in the paper. Below we lay out the process in detail for one dataset, and then provide the code for the other datasets below this. Note that much of this uses functions in the `simulations.R` file.

@@

## The latest version of dispRity on release branch #TG: master is under many changes!
## install_github("TGuillerme/dispRity", ref = "release")
library(dispRity)

@@

Heath et al bears
-----------

```{r}
slug <- "bears"

>>>>

This code runs the analyses in the paper. Below we lay out the process in detail for one dataset, and then provide the code for the other datasets below this. Note that much of this uses functions in the `simulations_fun.R` file.

@@

## The latest version of dispRity
## install_github("TGuillerme/dispRity", ref = "master")
library(dispRity)

@@
